Crop adaptation through gene flow

### 2016-07-13 Crop_adaptation_gene_flow_gj_outline_shortened.tex
Update Crop_adaptation_gene_flow_gj_outline_shortened.tex

\cite{rick1958role} summarizes morphological evidence of natural introgressive hybridization with wild relatives (specifically \emph{Solanum pimpinellifolium}) in South America, despite cultivated tomato's proclivity to self-pollinate.
However, these natural introgressions have yet be shown to be adaptive for the plant.
Also, \cite{hanson2000mapping} mapped a tomato yellow leaf curl virus resistance gene in an accession of \emph{S. habrochaites} f. \emph{glabratum} \cite{banerjee1990transfer} to an introgression on chromosome 11, which originated through breeding with the wild relative \emph{S. habrochaites}.

Similar resistance traits has also been shown to have been imparted from \emph{S. chilense}, \emph{S. pimpinellifolium}, and \emph{S. cheesmanii} \cite{hanson2000mapping}.
[[Dig deeper into these sources - evidence?  and naturally?]]

Since the work of Charles Rick in 1940s and 50s \cite{rick1953novel}\, breeding efforts have focused on incorporating and utilizing the relatively diverse genetic germplasm of wild tomato relatives \cite{rick1988tomato, miller1990rflp, rick1982potential}\.
Wild tomato relatives have been shown to harbor resistance genes for more than 40 agronomically important diseases, and breeders are working to introgress them into cultivated tomato \cite{rick1995utilization}\.

>>>>

\cite{rick1958role} summarizes morphological evidence of natural introgressive hybridization with wild relatives (specifically \emph{Solanum pimpinellifolium}) in South America, despite cultivated tomato's proclivity to self-pollinate.
However, these natural introgressions have yet been shown to be adaptive for the plant.
Since the work of Charles Rick in 1940s and 50s \cite{rick1953novel}\, breeding efforts have focused on incorporating and utilizing the relatively diverse genetic germplasm of wild tomato relatives \cite{rick1988tomato, miller1990rflp, rick1982potential}\.
Wild tomato relatives have been shown to harbor resistance genes for more than 40 agronomically important diseases, and breeders are working to introgress them into cultivated tomato \cite{rick1995utilization}\.
\cite{hanson2000mapping} mapped a tomato yellow leaf curl virus resistance gene in an accession of \emph{S. habrochaites} f. \emph{glabratum} \cite{banerjee1990transfer} to an introgression on chromosome 11, which originated through breeding with the wild relative \emph{S. habrochaites}.
Similar resistance traits has also been shown to have been imparted from \emph{S. chilense}, \emph{S. pimpinellifolium}, and \emph{S. cheesmanii} \cite{hanson2000mapping}.
